High-Performance Data Analysis on JANUS using Apache Spark

### 2013-12-18 paper.tex
Style!

Ten trials were performed for each test, allows us to compute average
runtimes. To compute the speedup, Spark runtimes were compared to the UNIX grep
command's serial runtime on the same file. Finally, during our first test on the
20 GB file, we evaluated performance using a different number of workers per
node. In Spark, a worker is an executor with it's own JVM which processes it's
own portion of the distributed data set. By default, a single worker is
employed on each node. For this test, we wanted to see if this was the ideal
setting for running Spark on JANUS.

@@

We have tested the scalability of Spark system on distributed Grep program and we still want to see whether for iterative algorithms, it's also scalable by looking at the time as the number of nodes increases.\\

@@

We test Bagel Pagerank on Dataset with 64,000 pages and 30 million links in total on four nodes in JANUS. As we limit the memory size from 1gb to 18gb in each node, the time is recorded. As shown in the Figure \ref{fig:insuff-mem}, the time stays stable when the memory limit is over 6gb since the program won’t use disk for RDD data storage. Once the memory limit is less than the memory required, the performance drops until it fails on one-node cluster, where the java heap exceeds the limit. Despite the performance degradation, it’s quite linear. Besides, the dataset size is 4.2gb and it consumes around 8.8gb memory per node, which is 35gb memory in total. one of the reasons is that Spark system designs the RDD to be immutable and every time a RDD is transformed, a new RDD is created, thus taking up lots of memory. The other reason is that Spark replicates the RDD on the go for loss of data.\\

>>>>

Ten trials were performed for each test, allows us to compute average
runtimes. To compute the speedup, Spark runtimes were compared to the UNIX grep
command's serial runtime on the same file. Finally, during our first test on the
20 GB file, we evaluated performance using a different number of workers per
node. In Spark, a worker is an executor with its own JVM which processes its
own portion of the distributed data set. By default, a single worker is
employed on each node. For this test, we wanted to see if this was the ideal
setting for running Spark on JANUS.

@@

@@

For comparison, we tested a Bagel implementation of PageRank on a dataset with
64,000 pages and 30 million links in total on four nodes in Janus. As we limit
the memory size from 1GB to 18GB in each node, the time is recorded. As shown
in the Figure \ref{fig:insuff-mem}, the time stays stable when the memory limit
is over 6GB since the program won’t use disk for RDD data storage. Once the
memory limit is less than the memory required, the performance drops until it
fails on one-node cluster, where the Java heap allocation is exceeded. Despite
the performance degradation, it's quite linear. Besides, the dataset size is
4.2GB and it consumes around 8.8GB memory per node, which is 35GB of memory in
total. One of the reasons is that RDDs are immutable and every time a RDD is
transformed, a new RDD is created, thus taking up lots of memory. The other
reason is that Spark replicates the RDD on the go for loss of data.
